Title

### 2023-05-04 paper/main.tex
Adding captions to figures

\usepackage{multicol}
\usepackage[margin=0.6in]{geometry}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Figure 1
\begin{figure*}[h]
	\centering
	\includegraphics{figure1.pdf}
	\caption{Caption 1}
	\label{fig:fig1}
\end{figure*}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Figure 2
\begin{figure}
	\centering
	% \includegraphics{Figures/Figure_lit_plat/Figure_lit_plat.pdf}
	\includegraphics{figure2.pdf}
	\caption{Caption.}
	\label{fig:fig2}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Figure 3
\begin{figure*}
	\centering
	\includegraphics{figure3.pdf}
	\caption{Caption}
	\label{fig:fig3}
\end{figure*}

@@

\begin{figure*}
	\centering
	\includegraphics{figure4.pdf}
	\caption{Caption}
	\label{fig:fig4}
\end{figure*}

@@

\begin{figure*}
	\centering
	\includegraphics{figure5.pdf}
	\caption{Caption}
	\label{fig:fig5}
\end{figure*}

@@

\subsection{Influence of volume fraction, $\phi$}

\begin{figure}
	\centering
	\includegraphics{figure6.pdf}
	\caption{Caption}
	\label{fig:fig6}
\end{figure}

>>>>

\usepackage{multicol}
\usepackage[textwidth=492.982pt, top=2cm, bottom=2cm]{geometry}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Figure 1
\begin{figure*}[h]
	\centering
	\includegraphics{figure1.pdf}
	\caption{\textbf{Experimental set-ups used in this study.} (a--c) Sketches of the three experimental set-ups. Below are shown snapshots of corresponding experimental images. (d--h) Set-up 1, $\alpha = 7^\circ$, $\phi \sim 3~\%$, $\mathcal{S}t=$ (i--k) Set-up 2, $\alpha = $, $\phi \sim $, $\mathcal{S}t=$ (l--p) Set-up 3, $\alpha = $, $\phi \sim $, $\mathcal{S}t=$.}
	\label{fig:fig1}
\end{figure*}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Figure 2
\begin{figure}
	\centering
	% \includegraphics{Figures/Figure_lit_plat/Figure_lit_plat.pdf}
	\includegraphics{figure2.pdf}
	\caption{\textbf{Explored parameter space.} Each symbol correspond to a single experimental run.}
	\label{fig:fig2}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Figure 3
\begin{figure*}
	\centering
	\includegraphics{figure3.pdf}
	\caption{(a) Current front position as a function of time for all experimental runs (b) Selected runs plotted in non-dimensional coordinates.}
	\label{fig:fig3}
\end{figure*}

@@

\begin{figure*}
	\centering
	\includegraphics{figure4.pdf}
	\caption{\textbf{Influence of the bottom slope.} (a) Current Froude number as a function of the bottom slope. (b) Current Froude number corrected by a prefector $\sqrt{a}$ as a function of the bottom slope. Here, plain symbols corresponds to $\phi < 0.45$, while transparent symbols are for $\phi \geq 0.45$ (see section~\ref{sec:influence_phi} for details on the influence of $\phi$).}
	\label{fig:fig4}
\end{figure*}

@@

\begin{figure*}
	\centering
	\includegraphics{figure5.pdf}
	\caption{\textbf{Influence of particle settling.} Current Froude number $\mathcal{F}r$ and non-dimensional quadratic dissipation $\tilde{\lambda}$ as a function of the ratio between the Stokes number and the lock aspect-ratio, for different ranges of bottom slopes. Here, we selected runs for $\phi < 0.45$ (see section~\ref{sec:influence_phi} for details on the influence of $\phi$).}
	\label{fig:fig5}
\end{figure*}

@@

\subsection{Influence of volume fraction, $\phi$}
\label{sec:influence_phi}

\begin{figure}
	\centering
	\includegraphics{figure6.pdf}
	\caption{\textbf{Influence of particle volume fraction.} Current Froude number as a function of the initial particle volume fraction for (a) $\alpha \approx 0^\circ$, and (b) $\alpha \approx 45^\circ$. The inset in (a) shows the plot in linear scale.}
	\label{fig:fig6}
\end{figure}
